a and generators

### 2022-05-10 documentos/intro.tex
Rev_Alejo

Quantum correlations~\cite{PhysicsPhysiqueFizika.1.195,
PhysRevLett.126.170404,Ollivier2001}, including entanglement~\cite{Horodecki},
are an important resource for a wide variety of tasks that
include teleportation~\cite{PhysRevLett.70.1895}, quantum
computation~\cite{nielsen_chuang_2011}, and others~\cite{Sapienza2019}.
However, this resource is also extremely delicate~\cite{nielsen_chuang_2011,Schlosshauer2004}, specially 
for multi-particle systems~\cite{Horodecki},  and important part
of the efforts of the community implementing quantum technologies is 
devoted to tackle this issue from an experimental \cite{Mooney_2021,Briegel1998} and
theoretical \cite{Bennett1996,Georgescu2020,RevModPhys.87.307} point of view. 
The process by which quantum correlations are unintentionally dissipated
is called decoherence~\cite{Schlosshauer2004,sep-qm-decoherence}.
One of the main tools to study the effects of decoherence are 
quantum channels. Quantum channels can describe quantum
noise~\cite{davalosdivisibility,ruskai}, open quantum systems
dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse
graining~\cite{Duarte2017,pinedacg}. 
%
% The identification of families of quantum channels among the whole convex set
% of quantum channels associated to a Hilbert space, is crucial to understand
% quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems
% dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse
% graining~\cite{Duarte2017,pinedacg}. 
One of the main difficulties to characterize quantum channels is that,
similar to quantum states, the parameters needed to describe them
increases overwhelmingly rapidly with the dimension of the Hilbert space.
%
Moreover, such parameters are constrained in a complicated way by 
physical conditions, such as complete positivity ~\cite{zimansbook}.
% Such parameters are not fully independent, the complete positivity condition imposes the regions that have physical meaning~\cite{zimansbook}.
% 
Describing in detail families of channels having a given property provides
insight into the jungle of quantum operations.
For the qubit case there are several studies concerning the unital case, for which
non-trivial properties can be described using only $3$ parameters, which in
turn form the well known tetrahedron of Pauli
channels~\cite{Rybar2012,ruskai,davalosdivisibility}. 
% For general
% finite-dimensional channels, several families of channels have been defined.
More generally, in~Ref.~\cite{nathanson2007pauli} the authors study families of 
convex combinations of quantum-classical channels that relate to
% have a close relation with 
unital qubit channels with positive eigenvalues, and give a
generalization of the Bloch sphere. 
% {\blue We will show later that some of the channels studied here are also
% quantum-classical.}\ddnote{Esta frase no me gusta, pero no se me occure nada
% mejor en tanto a la escritura. Propongo omitirla, despues se volvera a
% mencionar esto pero en donde corresponde.}
Similarly, a generalization of Pauli channels based on mutually unbiased
measurements is introduced and studied in Ref.~\cite{Siudzinska2020}. Other
studies of channels beyond the qubit can be
found~\cite{pub.1117408526,pub.1060516327,pub.1014660854}.
% \cpnote{Me gusta la idea de ir sobre un par de familias, pero no veo para que 
% mencionar a las MUBs aca, ni paraque introducir la sigla. Ojala podamos 
% discutir que familias mencionamos acá}\ddnote{atendido como fue acordado en la reunion :)}

>>>>

Quantum correlations~\cite{PhysicsPhysiqueFizika.1.195,
PhysRevLett.126.170404,Ollivier2001}, including entanglement~\cite{Horodecki},
are an important resource for a wide variety of tasks that
include teleportation~\cite{PhysRevLett.70.1895}, quantum
computation~\cite{nielsen_chuang_2011}, and others~\cite{Sapienza2019}.
However, this resource is also extremely delicate~\cite{nielsen_chuang_2011,Schlosshauer2004}, specially 
for multi-particle systems~\cite{Horodecki},  and important part
of the efforts of the community implementing quantum technologies is 
devoted to tackle this issue from an experimental \cite{Mooney_2021,Briegel1998} and
theoretical \cite{Bennett1996,Georgescu2020,RevModPhys.87.307} point of view. 
The process by which quantum correlations are unintentionally dissipated
is called decoherence~\cite{Schlosshauer2004,sep-qm-decoherence}.
One of the main tools to study the effects of decoherence are 
quantum channels. Quantum channels can describe quantum
noise~\cite{davalosdivisibility,ruskai}, open quantum systems
dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse
graining~\cite{Duarte2017,pinedacg}. 
%
% The identification of families of quantum channels among the whole convex set
% of quantum channels associated to a Hilbert space, is crucial to understand
% quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems
% dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse
% graining~\cite{Duarte2017,pinedacg}. 
One of the main difficulties to characterize quantum channels is that,
similar to quantum states, the parameters needed to describe them
increases overwhelmingly rapidly with the dimension of the Hilbert space.
%
Moreover, such parameters are constrained in a complicated way by 
physical conditions, such as complete positivity ~\cite{zimansbook}.
% Such parameters are not fully independent, the complete positivity condition imposes the regions that have physical meaning~\cite{zimansbook}.
% 
Describing in detail families of channels having a given property provides
insight into the jungle of quantum operations.
For the qubit case there are several studies concerning the unital case, for which
non-trivial properties can be described using only $3$ parameters, which in
turn form the well known tetrahedron of Pauli
channels~\cite{Rybar2012,ruskai,davalosdivisibility}. 
% For general
% finite-dimensional channels, several families of channels have been defined.
More generally, in~Ref.~\cite{nathanson2007pauli} the authors study families of 
convex combinations of quantum-classical channels that relate to
% have a close relation with 
unital qubit channels with positive eigenvalues, and give a
generalization of the Bloch sphere. 
% {\blue We will show later that some of the channels studied here are also
% quantum-classical.}\ddnote{Esta frase no me gusta, pero no se me occure nada
% mejor en tanto a la escritura. Propongo omitirla, despues se volvera a
% mencionar esto pero en donde corresponde.}
Similarly, a generalization of Pauli channels based on mutually unbiased
measurements is introduced and studied in Ref.~\cite{Siudzinska2020}. Other
studies of channels beyond the qubit can be
found~\cite{pub.1117408526,pub.1060516327,pub.1014660854,Fonseca2019}. \afnote{adicioné un paper mío donde trabajé con los flip-channels sobre qudits.}
% \cpnote{Me gusta la idea de ir sobre un par de familias, pero no veo para que 
% mencionar a las MUBs aca, ni paraque introducir la sigla. Ojala podamos 
% discutir que familias mencionamos acá}\ddnote{atendido como fue acordado en la reunion :)}

### 2022-05-10 documentos/pce.tex
Rev_Alejo

% \afnote{Propongo que cambiemos el inicio de esta sección por: 
In this section we introduce the family of Pauli component erasing (PCE)
maps. Let us start our discussion with a brief review of several basic concepts
of quantum channels that will allow us to introduce some notation, 
and finish with the definition of PCE maps, some generalities. We further 
introduce a useful graphical representation  for them.
% of the aforementioned maps. 
% and finish with the definition of PCE maps, some generalities and a graphical representation. 
% }
% In this section we introduce the definition of Pauli component erasing maps,
% but first we go through several standard definitions needed to discuss them.
\subsection{Quantum channels} \label{subsec:qtm_ch}% {{{
% \afnote{Creo que podríamos empezar la sección introduciendo el espacio de
% Hilbert y esas cosas y después si dedicarse solamente a Quantum channels. Si
% están de acuerdo, entonces sólo tendriamos que cambiar el orden de las dos
% primeras frases en el primer párrafo.}
Quantum channels are the most general linear operations that a quantum system
undergo independently of its past~\cite{zimansbook,cirac}.  The physical system
under study will be associated with a Hilbert space denoted by \hilbert{}, and
the set of linear operators over such space will be denoted by
$\mcB(\hilbert)$. That way, a density matrix $\rho$ of such system is an
element of $\mcB(\hilbert)$.
% \afnote{En esta última parte podriamos cambiar asi:}
% \afnote{The state of the physical system under study is associated to a
% Hilbert space \hilbert{}, and the set of linear operators over such space is
% denoted by $\mcB(\hilbert)$. In this way, a density matrix $\rho$ of such
% system is an element of $\mcB(\hilbert)$.}
% Quantum channels comprehend the most general linear operations that a quantum
% system undergo independently of its past~\cite{zimansbook,cirac}. To introduce
% their construction and properties, first let us define several objects. We will
% denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as
% $\hilbert_d$. The set of linear operators over a Hilbert space \hilbert will
% be written as $\mcB(\hilbert)$, and the set of density operators as $\mcS(\hilbert)$.
%, the subset of density matrices as
%$\mcS(\hilbert)$, which is in turn a subset of the so called trace-class
%operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied
%here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.

>>>>

% \afnote{Propongo que cambiemos el inicio de esta sección por: 
In this section we introduce the family of Pauli component erasing (PCE)
maps. Let us start our discussion with a brief review of several basic concepts
of quantum channels that will allow us to introduce some notation, 
and finish with the definition of PCE maps, some generalities \afnote{...and some generalities. (?)}. We further 
introduce a useful graphical representation  for them.
% of the aforementioned maps. 
% and finish with the definition of PCE maps, some generalities and a graphical representation. 
% }
% In this section we introduce the definition of Pauli component erasing maps,
% but first we go through several standard definitions needed to discuss them.
\subsection{Quantum channels} \label{subsec:qtm_ch}% {{{
% \afnote{Creo que podríamos empezar la sección introduciendo el espacio de
% Hilbert y esas cosas y después si dedicarse solamente a Quantum channels. Si
% están de acuerdo, entonces sólo tendriamos que cambiar el orden de las dos
% primeras frases en el primer párrafo.}
Quantum channels are the most general linear operations that a quantum system
undergo independently of its past~\cite{zimansbook,cirac}.  The physical system
under study will be associated with a Hilbert space denoted by \hilbert{}, and
the set of linear operators over such space will be denoted by
$\mcB(\hilbert)$. That way, a density matrix $\rho$ of such system is an
element of $\mcB(\hilbert)$.
% \afnote{En esta última parte podriamos cambiar asi:}
% \afnote{The state of the physical system under study is associated to a
% Hilbert space \hilbert{}, and the set of linear operators over such space is
% denoted by $\mcB(\hilbert)$. In this way, a density matrix $\rho$ of such
% system is an element of $\mcB(\hilbert)$.}
% Quantum channels comprehend the most general linear operations that a quantum
% system undergo independently of its past~\cite{zimansbook,cirac}. To introduce
% their construction and properties, first let us define several objects. We will
% denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as
% $\hilbert_d$. The set of linear operators over a Hilbert space \hilbert will
% be written as $\mcB(\hilbert)$, and the set of density operators as $\mcS(\hilbert)$.
%, the subset of density matrices as
%$\mcS(\hilbert)$, which is in turn a subset of the so called trace-class
%operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied
%here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.
